---
title: "Final Project: AirBnB New York City Analysis"
author: "Akira Nakagawa"
date: ""   
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r message = FALSE}
# -- Clear environment of variables and functions------------------
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)

# -- Load packages ---------------------------------------
library(tidyverse)
library(gridExtra)
library(janitor)
library(knitr)
library(GGally)
library(MultinomialCI)
library(htmlTable)
library(Hmisc)
library(formattable)
library(rms)
library(MultNonParam)
library(inspectdf)
library(DataExplorer)
library(leaflet)
library(ggmap)
ggmap::register_google(key = "AIzaSyDanbharxh0M9j1axst7NGeS1OnSXUf9WY")
library(htmltools)
library(colorspace)


library(readr)
fp <- read_csv("AB_NYC_2019.csv")

# make them factor variables
fp$id <- factor(fp$id)
fp$name <- factor(fp$name)
fp$host_id <- factor(fp$host_id)
fp$host_name <- factor(fp$host_name)
fp$neighbourhood_group <- factor(fp$neighbourhood_group)
fp$neighbourhood <- factor(fp$neighbourhood)
fp$room_type <- factor(fp$room_type)

# delete inactivated housing list
inactivated <- fp[ which(fp$price == 0 | fp$availability_365 == 0),]
fp <- subset(fp, fp$price > 0)
fp <- subset(fp, fp$availability_365 > 0)
# fp <- subset(fp, fp$price < 1500) # get rid of expensive data

# Add column "Listing history"
fp$list_history <- fp$number_of_reviews / fp$reviews_per_month 

# convert na values to 0s 
fp$reviews_per_month[is.na(fp$reviews_per_month)] <- 0

# create min_spend 
fp$min_spend <- fp$price * fp$minimum_nights

# delete id and host_id
delete <- c("id", "host_id")
fp[delete] <- NULL

# create borough area
manhattan <- subset(fp, fp$neighbourhood_group == "Manhattan")
brooklyn <- subset(fp, fp$neighbourhood_group == "Brooklyn")
bronx <- subset(fp, fp$neighbourhood_group == "Bronx")
queens <- subset(fp, fp$neighbourhood_group == "Queens")
staten <- subset(fp, fp$neighbourhood_group == "Staten Island")

```
<h2>Uni-variate non-graphical EDA</h2>
```{r message = FALSE, warning = FALSE}
# to look at the data 
head(fp)
```
<h4>Comments</h4>
<div>
- Some last_review does not have value - assuming there is no review for those rows
</div>

```{r message = FALSE, warning = FALSE}
# to see how many observations, variables, types etc
str(fp)
```
<h4>Comments</h4>
<div>
- negative longitude means West of the Prime Meridian
</div>
```{r}
summary(fp)
```
<h4>Comments</h4>
<div>
- categorical variables: neighbourhood_group, neighbourhood, room_type
- numerical variables: latitude, longtitude, price, minimum_nights, number_of_reviews, reviews_per_month,  calculated_host_listings_count, availability_365, list_history
- last_review: it has many NA values, it may be removed
- Most popular neighbourhood: Brooklyn(Williamsburg,Bedford-Stuyvesant, Bushwick), Manhattan (Harlem, Upper West Side, Hell's Kitchen)
</div>

<h2>Uni-variate graphical EDA</h2>
<h3>Categorical</h3>
All New York City
```{r}
grid.arrange(
# neighbourhood_group
ggplot(data = fp, mapping = aes(x = neighbourhood_group)) +
  geom_bar(),
# neighbourhood
ggplot(data = fp, mapping = aes(x = neighbourhood)) +
  geom_bar(),
# room_type
ggplot(data = fp, mapping = aes(x = room_type)) +
  geom_bar(),
ncol = 1)
```
Manhattan
```{r}
# Manhattan
grid.arrange(
# neighbourhood
ggplot(data = manhattan, mapping = aes(x = neighbourhood)) +
  coord_flip() +
  geom_bar(),
# room_type
ggplot(data = manhattan, mapping = aes(x = room_type)) +
  geom_bar(),
ncol = 2 )
```
Brooklyn
```{r}
# brooklyn
grid.arrange(
# neighbourhood
ggplot(data = brooklyn, mapping = aes(x = neighbourhood)) +
  coord_flip() +
  geom_bar(),
# room_type
ggplot(data = brooklyn, mapping = aes(x = room_type)) +
  geom_bar(),
ncol = 2 )
```
Bronx
```{r}
# brooklyn
grid.arrange(
# neighbourhood
ggplot(data = bronx, mapping = aes(x = neighbourhood)) +
  coord_flip() +
  geom_bar(),
# room_type
ggplot(data = bronx, mapping = aes(x = room_type)) +
  geom_bar(),
ncol = 2 )
```
Staten island
```{r}
# brooklyn
grid.arrange(
# neighbourhood
ggplot(data = staten, mapping = aes(x = neighbourhood)) +
  coord_flip() +
  geom_bar(),
# room_type
ggplot(data = staten, mapping = aes(x = room_type)) +
  geom_bar(),
ncol = 2 )
```

Frequency of categorical variables
```{r}
fp %>% 
  inspect_cat() %>% 
  show_plot()
```
<h4>Comments</h4> 
<div>
- Surprisingly, Manhattan has many Entire home/apt than any other parts of NYC.
- Brooklyn has almost the same amount of Entire home/apt and private room
- Bronx and Queens have more private room than Entire home/apt
- There are popular neighbour
</div>

<h3>Quantative</h3>
<h4>price</h4>
All NYC
```{r message = FALSE, warning = FALSE}
grid.arrange(
ggplot(data = fp, mapping = aes(x = price)) + 
    geom_histogram(),
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = price)) +
    coord_flip(), 
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>minimum_nights</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = fp, mapping = aes(x = minimum_nights)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = minimum_nights)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>number_of_reviews</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
ggplot(data = fp, mapping = aes(x = number_of_reviews)) + 
    geom_histogram(),
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = number_of_reviews)) +
    coord_flip(), # use to have same x-axis on both graphs
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>reviews_per_month</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = fp, mapping = aes(x = reviews_per_month)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = reviews_per_month)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>calculated_host_listings_count</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = fp, mapping = aes(x = calculated_host_listings_count)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = calculated_host_listings_count)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>availability_365</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = fp, mapping = aes(x = availability_365)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = availability_365)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>


<h4>list_history</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = fp, mapping = aes(x = list_history)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = fp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = list_history)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
- Many airbnb housing/room has been recently added (less than 3 years)
</div>
Show all numerical variables
```{r}
# Distribution of numeric variable 
fp %>% 
  inspect_num() %>% 
  show_plot()
```
<h4>Questions</h4> 
<div>
- It is hard to see the detail of price because there are some huge outliers
</div>


<h2>Multi-variate non-graphical</h2>
<h3>Categorical</h3>
neighbourhood_group & room_type
```{r}
fp %>% 
  tabyl(neighbourhood_group, room_type) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```
```{r}
fp %>% 
  tabyl(neighbourhood_group, room_type) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- 
</div>


neighbourhood & room_type
Manhattan
```{r}
# 
fp %>% 
  tabyl(neighbourhood, room_type) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```
```{r}
fp %>% 
  tabyl(neighbourhood, room_type) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- some neighbourhood has less than 30 observations
- Because most neighborhood has less than 1%, it is probably better to use neighbourhood_group instead, or just use most popular places for analysis
</div>


neighbourhood & neighbourhood_group
```{r}
fp %>% 
  tabyl(neighbourhood, neighbourhood_group) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```

```{r}
fp %>% 
  tabyl(neighbourhood, neighbourhood_group) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- There are too many neighbourhood, so the proportion for each neighbourhood is less than 1%
</div>


<h3>Quantitative</h3>
```{r message = FALSE, warning = FALSE}
# Correlation table
fp %>% 
  select_if(is.numeric) %>% # Use to select just the numeric variables
  cor() %>% 
  round(2) %>% 
  kable()


fp %>% 
  inspect_cor() %>% 
  show_plot()
```
<h4>Comments</h4> 
<div>
- calculated_host_listings_count and availability_365 has some correlations
- number_of_reviews and availability_365 has some correlations
</div>
<h4>Questions</h4> 
<div>
- 
</div>

<h2>Multi-variate graphical</h4>
<h3>Categorical</h3>
```{r}
grid.arrange(
  # neighbourhood_group and room_type
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, fill = room_type)) + 
      geom_bar(position = "dodge"),
ncol = 1
)
```
```{r}
grid.arrange(
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, fill = room_type)) + 
      geom_bar(position = "dodge") +
      coord_flip(),
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, fill = room_type)) +
      geom_bar(position = "fill") +
      coord_flip(),
ncol = 1
)
```
<h4>Comments</h4> 
<div>
- 
</div>

```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(neighbourhood_group, room_type)) + 
  geom_tile(aes(fill = count))

```
<h4>Comments</h4> 
<div>
- 
</div>
<h4>Questions</h4> 
<div>
- 
</div>

<h3>Quantitative</h3> 
```{r}
# price and minimum_nights
fp %>% 
  ggplot(mapping = aes(x = price, y = minimum_nights)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- It seems they do not have any relationship
</div>


```{r}
# price and number_of_reviews
fp %>% 
  ggplot(mapping = aes(x = price, y = number_of_reviews)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- It seems they do not have any relationship
</div>

```{r}
# price and reviews_per_month
fp %>% 
  ggplot(mapping = aes(x = price, y = reviews_per_month)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- This may have more relationship than number of total review and price
</div>


```{r}
# price and availability_365
fp %>% 
  ggplot(mapping = aes(x = price, y = availability_365)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- This may have relationship
</div>

```{r}
# calculated_host_listings_count and availability_365
fp %>% 
  ggplot(mapping = aes(x = calculated_host_listings_count, y = availability_365)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- This may have relationship
</div>

```{r}
# calculated_host_listings_count and minimum_nights
fp %>% 
  ggplot(mapping = aes(x = calculated_host_listings_count, y = minimum_nights)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- This may have relationship
</div>

```{r}
# longitude and latitude
fp %>% 
  ggplot(mapping = aes(x = longitude, y = latitude)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- Definitely the map of new york city
- Some places does not have any listing
</div>


<h3>Categorical and quantitative</h3> 

```{r warning = FALSE, message = FALSE}
fp %>%
  select(neighbourhood_group, room_type, price, minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, availability_365) %>%
  ggpairs()

# Correlation of variables 
fp %>% 
  plot_correlation(maxcat = 5L)

```

<h4>Comments</h4> 
<div>
- Looking more closely 
  - neighbourhood_group / top neighbourhood of the group with other variables
  - 
</div>


```{r message = FALSE, warning = FALSE}
# minimum_nights, price and neighbourhood_group
fp %>% 
    ggplot(mapping = aes(x = minimum_nights, y = price, color = neighbourhood_group)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)

# availability_365, price and neighbourhood_group
fp %>% 
    ggplot(mapping = aes(x = availability_365, y = price, color = neighbourhood_group)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)

# reviews_per_month, price and neighbourhood_group
fp %>% 
    ggplot(mapping = aes(x = reviews_per_month, y = number_of_reviews, color = neighbourhood_group)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)

# availability_365, calculated_host_listings_count and neighbourhood_group
fp %>% 
    ggplot(mapping = aes(x = availability_365, y = calculated_host_listings_count, color = neighbourhood_group)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)

```
<h4>Comments</h4> 
<div>
- Almost all neighbourhood_group have the similar correlation pattern
- Manhattan has more correlation with availability_365 and calculated_host_listings_count
</div>


```{r}
grid.arrange(
  # neighbourhood_group and price
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, y = price)) +
      geom_boxplot(),
  # room_type and price
  fp %>% 
    ggplot(mapping = aes(x = room_type, y = price)) +
      geom_boxplot(),
  # neighbourhood_group and minimum_nights
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, y = minimum_nights)) +
      geom_boxplot(),
  # room_type and minimum_nights
  fp %>% 
    ggplot(mapping = aes(x = room_type, y = minimum_nights)) +
      geom_boxplot(),
  
  # neighbourhood_group and number_of_reviews
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, y = number_of_reviews)) +
      geom_boxplot(),
  # room_type and number_of_reviews
  fp %>% 
    ggplot(mapping = aes(x = room_type, y = number_of_reviews)) +
      geom_boxplot(),
  
  # neighbourhood_group and reviews_per_month
  fp %>% 
    ggplot(mapping = aes(x = neighbourhood_group, y = reviews_per_month)) +
      geom_boxplot(),
  # room_type and reviews_per_month
  fp %>% 
    ggplot(mapping = aes(x = room_type, y = reviews_per_month)) +
      geom_boxplot(),
  
ncol = 2
)

```
<h4>Comments</h4>
<div>
- 
</div>



```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(med_price = median(price)) %>% 
  ggplot(aes(neighbourhood_group, room_type)) +
  geom_tile(aes(fill = med_price))

```



```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(med_nights = median(minimum_nights)) %>% 
  ggplot(aes(neighbourhood_group, room_type)) +
  geom_tile(aes(fill = med_nights))
```
```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(med_reviews = median(number_of_reviews)) %>% 
  ggplot(aes(neighbourhood_group, room_type)) +
  geom_tile(aes(fill = med_reviews))
```


```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(med_month_reviews = median(reviews_per_month)) %>% 
  ggplot(aes(neighbourhood_group, room_type)) +
  geom_tile(aes(fill = med_month_reviews))
```

```{r}
fp %>%
  group_by(neighbourhood_group, room_type) %>% 
  summarise(med_lists = median(calculated_host_listings_count)) %>% 
  ggplot(aes(neighbourhood_group, room_type)) +
  geom_tile(aes(fill = med_lists))
```
<h4>Comments</h4>
<div>
- Manhattan's Entire home is the most expensive median, but number of reviews of Manhattan's entire place has one of the lowest. 
</div>


<h4>Questions</h4>
<div>
- What makes some housing list extremely expensive?
- More investigation on the map
- More investigation on the top neighbourhood characteristics
</div>



<h2>Detailed EDA </h2>
What is the price distribution?
```{r}
ggplot(fp, aes(price)) +
  geom_histogram(bins = 30, aes(y = ..density..)) + 
  geom_density(alpha = 0.5) +
  geom_vline(xintercept = mean(fp$price), size = 2, linetype = 3) +
  annotate("text", x = 1800, y = 0.75,label = paste("Mean price = ", paste0(round(mean(fp$price), 2))),
           color =  "#32CD32", size = 8) +
  scale_x_log10(breaks = seq(0, 10000, 100))

```
<h4>Comments</h4>
<div>
- How about by the neighbourhood_groups?
</div>


```{r}
neighbor_mean <- fp %>%
  group_by(neighbourhood_group) %>%
  summarise(price = round(mean(price), 2))

ggplot(fp, aes(price)) +
  geom_histogram(bins = 30, aes(y = ..density..)) + 
  geom_density(alpha = 0.2) +
  ggtitle("Transformed distribution of price\n by neighbourhood groups",
          subtitle = expression("With" ~'log'[10] ~ "transformation of x-axis")) +
  geom_vline(data = neighbor_mean, aes(xintercept = price), size = 2, linetype = 3) +
  geom_text(data = neighbor_mean,y = 1.5, aes(x = price + 1400, label = paste("Mean  = ",price)), color = "darkgreen", size = 4) +
  facet_wrap(~neighbourhood_group) +
  scale_x_log10() 

```
<h4>Comments</h4>
<div>
- We can see all the neighbourhood_group have skewed mean even when applying log transformation
- Manhattan has highest mean of 214.2
</div>


```{r}
fp %>% filter(price >= mean(price)) %>% group_by(neighbourhood_group, room_type) %>% tally %>% 
  ggplot(aes(reorder(neighbourhood_group,desc(n)), n, fill = room_type)) +
  xlab(NULL) +
  ylab(NULL) +
  ggtitle("Number of above average price listings",
          subtitle = "Most of them are entire homes or apartments") +
           geom_bar(stat = "identity")

```
<h4>Comments</h4>
<div>
- Visually I cannot see anything Shared room over the average
- remember except Manhattan, all the neighbourhood_group have more private room
- However, for the price above average, there are more entire home consisted
- Entire home can create 
</div>

More interested in room_type
```{r}
fp %>%
  group_by(neighbourhood_group) %>%
    ggplot(aes(x = room_type, y = price)) +
      geom_boxplot(aes(fill = room_type)) + scale_y_log10() +
      xlab("Room type") + 
      ylab("Price") +
      ggtitle("Boxplots of price by room type",
              subtitle = "Entire homes and apartments have the highest avg price") +
      geom_hline(yintercept = mean(fp$price), color = "purple", linetype = 2)

```

How does it look like with median of room_type and neighbourhood
```{r}
# Median of price by Room type
med_price <- fp %>% group_by(neighbourhood_group, room_type) %>% summarise(med_price = median(price ), n = n())
med_price %>% ggplot(aes(x = neighbourhood_group, y = med_price, fill = paste(room_type))) + 
  geom_bar(stat = 'identity', position = 'dodge')  
```

```{r}
# Median of minimum_nights by Room type
med_nights <- fp %>% group_by(neighbourhood_group, room_type) %>% summarise(med_night = mean(minimum_nights),n = n())
med_nights %>% ggplot(aes(x = neighbourhood_group, y = med_night, fill = paste(room_type))) + 
  geom_bar(stat = 'identity', position = 'dodge')  
```

```{r}
# Median of minimum cost (price*minimum_nights)s by Room type
med_min_spend <- fp %>% group_by(neighbourhood_group, room_type) %>% summarise(med_cost = median(price * minimum_nights),n = n())
med_min_spend %>% ggplot(aes(x = reorder(neighbourhood_group, -med_cost), y = med_cost, fill = paste(room_type))) + 
  geom_bar(stat = 'identity', position = 'dodge')+
  labs(x ="", y="", title = "Entire Room listings of Manhattan's minimum spending is outstanding", subtitle = "About double as Brooklyn's entire home", caption = "From Technical Appendix") +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  scale_y_continuous(breaks = seq(0, 900,200), labels = scales::dollar) +
  scale_fill_discrete_qualitative(palette = "Cold") +
  ggsave("min_spend.png")

```
<h4>Comments</h4>
<div>
- as assumed, the manhattan's Entire room has the highest median
- Manhattan's private room is cheaper than other neighbourhood_group's Entire home
- Shared room in Staten Island is surprisingly more expensive than the private room median
- It looks Private room to Shared room does not have much decrease in median revenue 
</div>
<br>
Let's see it on the map
```{r}
fp %>% 
  ggplot(aes(longitude, latitude)) + 
  geom_hex() + 
  scale_fill_gradient(low = 'yellow', high = 'red', breaks = c(500, 1000)) + 
  labs(x = 'Longitude', y = 'Latitude') + 
  facet_wrap(~ room_type) + 
  theme(legend.position = 'bottom')
```
<h4>Comments</h4>
<div>
- It is hard to even see the Shared room whereas Entire home and private room are located mostly in Manhattan area and Brooklyn
</div>
Median price by neighbourhood
```{r}
neighbour_median <- fp %>%
  group_by(neighbourhood) %>%
  summarise(median(price))
colnames(neighbour_median)[2] <- "med_price_neighbour"
fp_subset <- merge(fp, neighbour_median)
```

```{r}
staten$neighbourhood[staten$price == 800]
```


```{r}
fp_subset <- subset(fp_subset, neighbourhood != "Fort Wadsworth")
save_p_1 <- ggmap(get_googlemap(center = c(lon = -73.95, lat = 40.72),
                    zoom = 11, scale = 4,
                    maptype ='terrain',
                    color = 'color')) +
  geom_point(aes(x = longitude, y = latitude,  colour = med_price_neighbour), data = fp_subset, size = 0.1) + 
  scale_colour_gradientn(colours = rainbow(3)) +
  labs(x = "", y = "", title = "Lower Manhattan has the highest central tendency of price ", subtitle = "Surprisingly Upper East/West side and Brooklyn seem to be similar in price range", caption = "From Technical Appendix", col="Price Range in USD") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank()
        )
save_p_1
ggsave(filename = "geo.png", plot = save_p_1)

```
<h4>Comments</h4>
<div>
- Financial district to midtown has higher price range compared to the upper east/west side and northern area of manhattan
- There is one blue spot (highest median price) in Staten Island 
</div>


```{r}

pal <- colorNumeric(
  palette = "Blues",
  domain = fp$med_price_neighbour)

leaflet(options = leafletOptions(minZoom = 0, maxZoom = 18)) %>% 
  setView(lng = -73.95, lat = 40.72, zoom = 12)  %>% 
    addMarkers(data = fp, lat = ~ latitude, lng = ~ longitude, clusterOptions = markerClusterOptions(), label = ~htmlEscape(name), 
               popup = paste("Price per night: $", fp$price, "<br>",
                           "Room Type:", fp$room_type, "<br>",
                           "Minimum Stay:", fp$minimum_nights, "days<br>", 
                           "Minimum Cost for stay: $", fp$minimum_nights * fp$price, "<br>",
                           "Monthly Average Number of Reviews: ", fp$reviews_per_month)
               ) %>% 
  addTiles() 



```
<h4>Comments</h4>
<div>
- Usuful for the dashboard
</div>


<h2>Stats EDA </h2>
Does Room_type impact the price?
```{r}
(t <- t.test(fp$price[fp$room_type == 'Entire home/apt'], fp$price[fp$room_type == 'Private room' ], conf.level = 0.95))
```
```{r}
(t <- t.test(fp$price[fp$room_type == 'Entire home/apt'], fp$price[fp$room_type == 'Shared room' ], conf.level = 0.95))
```

```{r}
(t <- t.test(fp$price[fp$room_type == 'Private room'], fp$price[fp$room_type == 'Shared room' ], conf.level = 0.95))
```
<h4>Comments</h4>
<div>
- reject the null hypothesis that the room type does not impact the price
</div>


```{r}
z <- qnorm(0.975) #95 percent

fp %>%
  group_by(room_type) %>%
  summarise(mn = mean(price), sd = sd(price), n = n(), ci = z * sd/sqrt(n)) %>%
  ggplot(aes(x = room_type, y = mn)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mn - ci, ymax = mn + ci), width = 0.5, position = position_dodge(0.9)) +
  labs(title = "Price difference by Room type with error bar")

```


```{r}
chisq.test(table(fp$neighbourhood_group, fp$room_type))

```
<h4>Comments</h4>
<div>
- X-square is large,so reject the null
- P-value is small, so reject the null
- According to the test,we cannot see what is different and what is similar
</div>


How do neighbourhood_group's listing price vary with room_type
```{r}
C_P_n <- fp %>%
  group_by(neighbourhood_group, room_type) %>%
  summarise(n = n())

C_P_n_ci <- multinomialCI(t(C_P_n[, 3]), 0.05)

C_P_tab <- fp %>%
  group_by(neighbourhood_group, room_type) %>%
  summarise(prop = round(n()/sum(nrow(fp)), 3))

C_P_tab$ci_l <- round(C_P_n_ci[,1], 3)
C_P_tab$ci_u <- round(C_P_n_ci[,2], 3)

htmlTable(C_P_tab)

```
```{r}
# Graph of proportions with confidence intervals
C_P_tab %>% 
  ggplot(aes(x = room_type, y = prop, fill = neighbourhood_group)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_text(aes(label = round(prop, 2)), vjust = -4, color = "black", # vjust moves lables above CI
            position = position_dodge(0.9), size = 4) +
  geom_errorbar(aes(ymin = ci_l, ymax = ci_u), 
                width = 0.4, position = position_dodge(0.9))

```
<h4>Comments</h4>
<div>
- Proprotionally Manhattan, Brooklyn and Queens are more reliable in any room_type 
</div>


Significance of Correlation
```{r}
fp %>% 
  select_if(is.numeric) %>% 
  as.matrix() %>% 
  rcorr()
```
Multi-linear regression
```{r}

# logistic regression with general linear model (glm)
mod <- glm(factor(price) ~ neighbourhood_group + room_type + minimum_nights + number_of_reviews + availability_365, 
           family = binomial(link='logit'), 
           data = fp)

# Review output
summary(mod)

```
<h4>Comments</h4>
<div>
- Manhattan, Brooklyn has more impact on price
</div>

Residuals of the model
```{r}
par(mfrow = c(1, 1))
# price
plot(fp$price, mod$residuals)

```
```{r}
# neighbourhood_group
plot(fp$neighbourhood_group, mod$residuals)
```
```{r}
# neighbourhood
plot(fp$neighbourhood, mod$residuals)
```
```{r}
# room_type
plot(fp$room_type, mod$residuals)
```

```{r}
# minimum_nights
plot(fp$minimum_nights, mod$residuals)
```
```{r}
# number_of_reviews
plot(fp$number_of_reviews, mod$residuals)
```

Visualization of Multiple Regression
```{r}
coe <- summary(mod)$coefficients # get coefficients and related stats
coe_CI <- as.data.frame(cbind(coe[-1, ], confint(mod)[-1, ])) # find and bind CI, remove Intercept 

names(coe_CI) <- c("estimate", "se", "t", "pval","low_CI","high_CI") 

# Order base on p-value
htmlTable(round(coe_CI[order(coe_CI$pval, decreasing = FALSE), ], 3))
```
```{r}
# reorder by p-value
(g1 <- ggplot(coe_CI, aes(x = estimate, y = reorder(row.names(coe_CI),desc(pval)))) +
  geom_point(size = 3) +
  xlim(min(coe_CI$low_CI), max(coe_CI$high_CI)) +
  ylab("Variable") +
  xlab("Coefficient") +
  theme_bw() 
)

```
```{r}
# Use geom_segment to illustrate CI
(g2 <- g1 +
  geom_vline(xintercept = 0, color = "red")) +
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(pval))), 
               xend = coe_CI$high_CI, color = "Blue") +
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(coe_CI$pval))), 
               xend = coe_CI$low_CI, color = "Blue") +
  xlab("Coefficient with Confidence Interval") 

```
<div>
- Shared Room(room_type) and Staten Island (neighbourhood_group) have interesting confidence interval
- in the non-graphical, we cannot see the upper bound of confidence interval for those two
</div>


<h2>Summary</h2>
<h4>Comments</h4>
<div>
- Manhattan has the highest price with Entire home/apartment
  - Manhattan's Entire home/apartment's minimum spending is extremely higher than the other neighbourhood in new york
- From the map, particularily Brooklyn area is high as in upper manhattan
- Problems on the data
  - does not have the size of listing's living area
  - more detail information may be required to get in order to do more investigation
</div>





